### 2023-02-10 article.tex
Progress

Again, useful paradata should be comprehensive, 
documented appropriately, the documentation should co-evolve with the data,
and the data should be friendly to computers \cite{huvila2022improving}.
In this section, these ideal properties of paradata are applied to code.
Code as paradata, however, has multiple uses as well,
which are to reproduce, to replicate and to 
extend a computational experiment \cite{benureau2018re}.
In this section, the recommendations how to make paradata useful
is applied to code and compared to existing best practices in software 
development, for the intended use of the code.

@@

For purposes of reproducing (same code, same data) or replicating (same code,
different data) a study, the minimal amount of documentation
is determined by software development best practices.
When an independent researcher reproduces or replicates an experiment, 
it is possible (even ideal!) that no code is read at all.
However, the use of the code should be documented,
as 57\% out of 56 Science magazine corresponding authors 
that shared their code
has documented their code well enough to run it 
and understand what it ought to do \cite{stodden2018empirical}.
When one is able to run the code, it could argued 
that no further documentation is needed.
However, all code in general should be documented 
'adequately' \cite{peng2006reproducible},
ideally writing code in such a way that it becomes 
self-explanatory \cite{wilson2014best}
and for the remaining code to document the reasons behind it, 
its design and its purpose \cite{wilson2014best}.

@@

For code to be ideal paradata, 
its creation and documentation need to match, 
'not least because they shape each other' \cite{huvila2022improving}.
This quote resonates strongly with the idea of 
literate programming \cite{knuth1984literate},
in which documentation and code is developed hand-in-hand.
rOpenSci, a community that, among others, reviews programming
code (\cite{ram2013ropensci,ram2018community}), is 
one example of where literate programming is enforced:
code must have extensive runnable examples
as part of the documentation \cite{ropensci_2021_6619350}.
Developing code and documentation at the same time 
leads to both better code and documentation \cite{reenskaug1989environment}.
In general, when developing software, 
it is recommended to 
to write documentation while writing software,
as well as to include many examples \cite{lee2018ten}.

>>>>

Again, useful paradata should be comprehensive, 
documented appropriately and in co-evolvution with the data,
and the data should be friendly to computers \cite{huvila2022improving}.
In this section, these ideal properties of paradata are applied to code.
Code as paradata, however, has multiple uses as well,
which are to reproduce, to replicate and to 
extend a computational experiment \cite{benureau2018re}.
In this section, the recommendations how to make paradata useful
is applied to code and compared to existing best practices in software 
development, for the intended use of the code.

@@

For purposes of reproducing (same code, same data) code,
it should at least be documented how the code is run.
However, 57\% out of 56 Science magazine corresponding authors 
that shared their code has documented their code well enough to run it 
and to be understood what it ought to do \cite{stodden2018empirical}.

However, when an independent researcher can redo an experiment, 
it is possible (even ideal!) that no code is read at all.
Within that context, it could argued that no further documentation is needed.
However, all code in general should be documented 
'adequately' \cite{peng2006reproducible},
ideally writing code in such a way that it becomes 
self-explanatory \cite{wilson2014best}
and for the remaining code to document the reasons behind it, 
its design and its purpose \cite{wilson2014best}.

@@

For code to be ideal paradata, 
its creation and documentation need to align, 
\emph{not least because they shape each other} \cite{huvila2022improving}.
This emphasized part of the quote resonates strongly with the idea of 
literate programming \cite{knuth1984literate},
in which documentation and code is developed hand-in-hand.
It is the practice of writing a document mixed with code that 
will be run.
Contemporary examples of this idea are, among others, 
vignettes \cite{wickham2015r} (for the R programming language \cite{r}) 
and Jupyter notebooks \cite{wang2020assessing} 
(for the Julia \cite{Julia-2017}, Python \cite{van1995python} and R \cite{r}
programming languages).
rOpenSci, a community that, among others, reviews programming
code (\cite{ram2013ropensci,ram2018community}), is 
one example of where literate programming is enforced:
code must have extensive runnable examples
as part of the documentation \cite{ropensci_2021_6619350}.
Developing code and documentation at the same time 
leads to both better code and documentation \cite{reenskaug1989environment}.
In general, when developing software, 
it is recommended to 
to write documentation while writing software,
as well as to include many examples \cite{lee2018ten}.
